### 2019-08-24 manuscript/abstract.tex
- Removed old comments and rearranged one sentence of Summary

% max 200 words (188 now)
\begin{itemize}

@@

% Methods
\item To extensive trait and phylogenetic data in Solanaceae, we fit twenty-nine diversification models to investigate how speciation and extinction rate differences are associated with ploidy, breeding system, and the interaction between these traits.
% \item  We investigate the effect of ploidy and breeding system, including their interaction, and unobserved traits, on speciation and extinction rates in Solanaceae by fitting and comparing twenty-nine diversification models.

% Results
\item We show that diversification patterns in Solanaceae are better explained by breeding system and an additional unobserved factor, rather than by ploidy.  % E: changed because we don't show that breeding system and one hidden trait are sufficient
%These results are largely robust to allowing for diploidization.  %B: I now dropped it again to squeeze under 200 words. %B: this sentence was apparently accidentally dropped? % I removed the diploidization because the story was complicated so I preferred not to add it in the abstract
We also find that the most common evolutionary pathway to polyploidy in Solanaceae occurs via direct breakdown of self-incompatibility by whole-genome duplication, rather than indirectly via breakdown followed by polyploidization.

% Conclusions
\item Comparing multiple stochastic diversification models that include complex trait interactions alongside hidden states enhances our understanding of the macroevolutionary patterns in plant phylogenies.  %B was: We show that modeling complex trait interactions is key to our understanding of diversification.

>>>>

% presently 187/200 words
\begin{itemize}

@@

% Methods
\item  We fit twenty-nine diversification models to extensive trait and phylogenetic data in Solanaceae and investigate how speciation and extinction rate differences are associated with ploidy, breeding system, and the interaction between these traits.%B: I re-ordered this and removed the second "to": To extensive trait and phylogenetic data in Solanaceae, we fit twenty-nine diversification models to investigate how speciation and extinction rate differences are associated with ploidy, breeding system, and the interaction between these traits.

% Results
\item We show that diversification patterns in Solanaceae are better explained by breeding system and an additional unobserved factor, rather than by ploidy. 
We also find that the most common evolutionary pathway to polyploidy in Solanaceae occurs via direct breakdown of self-incompatibility by whole-genome duplication, rather than indirectly via breakdown followed by polyploidization.

% Conclusions
\item Comparing multiple stochastic diversification models that include complex trait interactions alongside hidden states enhances our understanding of the macroevolutionary patterns in plant phylogenies.
